---
title: "Parallel Computing"
author: "Aphinda Jabe"
format: html
editor: visual
---

```{r}
#| warning: false
#| message: false

library(foreach)
library(doParallel)
library(MASS)
library(parallel)
library(iterators)
library(flextable)
```

## Question 1

```{r}

mean_vect <- function(x){
  return(mean(x))
}

var_vect <- function(x){
  return(var(x))
}

rand_exp <- foreach(i = 1:100, .combine = rbind) %do% { 
  s <- rexp(100)
  c(Mean = mean_vect(s), Variance = var_vect(s))
}

flextable(as.data.frame(rand_exp))
```

## Question 2

```{r}
#|warning: false
 
clusts <- makeCluster(3)
registerDoParallel(clusts)

system.time({
boot_result <- foreach(i = 1:1000,.combine = c, .packages = 'MASS') %dopar% { 
  median(sample(galaxies, size = length(galaxies), replace = TRUE))}

})

stopCluster(clusts)
boot_median <- mean(boot_result)
boot_median
```

**Testing with bigger chunks**

```{r}

clusts_2 <- makeCluster(3)
registerDoParallel(clusts_2)

system.time({
boot_result <- foreach(i = 1:10,.combine = c, .packages = 'MASS') %dopar% {
  replicate(100,
  median(sample(galaxies, size = length(galaxies), replace = TRUE))
)}

})

stopCluster(clusts_2)
boot_median <- mean(boot_result)
boot_median
```

Increasing the size of the chunks reduced the overheads, making it more efficient compared to running individual bootstrap iterations.

## Question 3

```{r}

true_mean = 1

coverage <- replicate(1000, {
boot_s <- rexp(50)
boot_means <- replicate(1000, 
  mean(sample(boot_s, 50, replace = TRUE)))

CI <- quantile(boot_means, probs = c(0.025, 0.975))

(true_mean >= CI[1]) & (true_mean <= CI[2])} )

mean(coverage)

```

## Question 4

```{r}
set.seed(1234)


system.time({
outcome <- foreach(x = irnorm(5, count = 3), .combine = c) %do% {max(x)}

})
outcome
```

## Question 5

**Using the parLapply() to solve Q4**

```{r}


cl <- makeCluster(3)

system.time({
c <- parLapply(cl, 1:3 , function(a){
  x <- rnorm(5)
  max(x)})
})

stopCluster(cl)
c
```

**Use replicate()**

```{r}

system.time({
max_values <- replicate(3, max(rnorm(5)))
})

max_values

```

3 different methods were used to complete question 4 and compare the times taken. Parallel computing method - parLappy() recorded the highest time, followed by foreach() and lastly replicate().
